---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# r4es

<!-- badges: start -->
<!-- badges: end -->

r4es contains code tutorials on using R for working with environmental data. These tutorials are the first steps to the eventual book, [R for Environmental Science](https://github.com/corysauve/r4es-book). 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("corysauve/r4es")
```

## Available tutorials 

All tutorials and datasets are included when r4es is installed. They are also found under **
```{r example}
library(r4es)
## basic example code
```

## Contributing 

I welcome any contributions or suggestions for improving this package! Please open an issue to do so. 

## License 

The r4es package is licensed under the MIT License. Please see the [LICENSE](LICENSE.md) for more details.
